Universal Anonymous Signatures

### 2022-08-21 prism-backend/research/gsac/formal-uas.tex
Pass on main body.

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, signers (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Finally, we incorporate functions that
allow tweaking the conditions checked at credential issuance and signature
generation times, including the information that an opener will be able to
extract from a signature.

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage their keys to request credentials.
Therefore, if one ``user'' generates (e.g.) two keys, and then uses each of
these keys to request multiple credentials, then from the point of view of our
modelling, we see this \emph{cryptographically} as two different users.
This may seem too ideal to model real world situations. However, we argue that
this can in fact be very close to reality, where a well-known issuer, after
properly identifying a user, attests the (possibly blinded) public key this
user proves control of. Indeed, our model and syntax support exactly this
approach, by allowing users to leverage previously obtained credentials in
order to request new ones.

\paragraph{Users and issuers.} %
Finally, a relevant aspect of our approach is that users and issuers are
essentially the same thing: just an entity with a key pair. The difference is
that, when users wish to become issuers, they have to advertise their public
keys, along with their conditions for granting credentials. For simplicity, we
just assume that they somehow ``publish their public keys''. In practice, this
may be done in several ways, depending on the situation: self-signing, relying
on external PKIs, bulletin-boards, etc.
%
This approach has actually been used before to model delegatable anonymous
credentials \cite{bcc+09}, and it turns out to be also very useful for our
approach to build ring signatures from \UAS.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans$ being the transcript
  of the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a plaintext value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We introduce three functions in our syntax and model. Through them,
it is possible to modulate the behaviour of the resulting instantiation, by
controling the conditions upon which a new credential can be issued, the
information revealed at signing time, or after signing. In all cases, it is
the user who computes them, and has to prove correctness of such computation.
We give concrete examples in \secref{sec:relationships}, and define them next:

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]},\attrs)
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  over attributes \attrs, when requested by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied.
  \fissue functions must be \UAS-acceptable, as defined in
  \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. $\yeval^0$ is output directly alongside the
  signature,  both can in addition be used to modulate the behaviour of
  \finsp, and must belong in a well defined set \rngfeval. For readability,
  we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\lbrace (\cidi,\cattrs_i)
      \rbrace_{i\in[n]},\attrs) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
and for openers, \oid. Although issuers are ``extended'' users, and thus can be
identified by their \uid, we also sometimes use \iid to refer to a user acting
as issuer, especially, for operations involving both a user and an issuer (this
also applies for key pairs).
%
All tables/sets are initialized as empty tables/sets. For notational
convenience, we often use these identifiers instead of the corresponding
user/issuer/opener keys.
%
We use the following sets and tables in our definitions:

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\HUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting its evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' an user to become an issuer, specifying its
  \fissue function.
\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures using credentials from honest
  users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],\PRVUK[\cuid_0],\cscid_0,\attrs)) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],\PRVUK[\cuid_1],\cscid_1,\attrs)):
          \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\PRVUK[\uid],\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

The issuance anonymity game captures that, during credential issuance
interactions, the adversary gains no information about the
user(s) behind them. For this, we allow the adversary to control targetted
issuers and openers (although it may also add honest ones), and add honest and
corrupt users. The adversary can also obtain credentials, produce signatures,
and open them. We need to make some limitations to prevent trivial wins: first,
when querying the oracle for obtaining a challenge credential out of two
possible user-credential set pairs, the issuance protocol must either succeed or
fail for both; also, the adversary can open signatures produced with credential
sets containing challenge credentials $\cred_b$, only if the output of \Open is
the same as with the complementary $\cred_{1-b}$ (note that any other signature
can be opened).
Intuitively, if the adversary cannot distinguish arbitrary runs with all oracles
(provided the previous constraints) when he gets challenge credentials
$\cred_b$, from runs with credentials $\cred_{1-b}$, then the issuance protocol
is privacy-preserving.

@@

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations:
$\NIZKRel_{\Issue}$, $\NIZKRel_{\Sign}$, and $\NIZKRel_{\Open}$, described next
and specified in CS notation \cite{cs97} in \figref{fig:nizkrels}.

>>>>

The main contribution of this section is giving a simple syntax and model that
still allow spanning a wide variety of related schemes. We combine aspects of GS
and AC schemes, generalizing whenever possible. Like in ACs, there are multiple
issuers, and each user can get one or more credentials from any of them; and,
also, use more than one credential simultaneously to produce a signature. We
incorporate openers, as in GSs, but there is no tight relationship between
issuer and opener. As a consequence, users (potentially along with verifiers)
may choose, on a per-signature basis, the policies governing the utility
information extractable from a signature. Finally, we incorporate functions that
allow tweaking the conditions checked at credential issuance and signature
generation times, including the information that an opener will be able to
extract from a signature.

\paragraph{Users and credentials.} %
We model a scheme in which every single user may have multiple credentials.
Moreover, previously obtained credentials can be leveraged simultaneously to
obtain a new one. In this setting, a perhaps too strict assumption we make is
that, once a user gets compromised, all of the credentials owned by that user
are compromised too. While there may be real world situations for which this is
too aggressive, it is certainly a worst-case scenario, and greatly simplifies
the modelling.
%
Somehow related, we model a scheme in which users generate their secret keys in
a standalone way, and then leverage these keys to request credentials. This may
seem too ideal as a model for real world situations, as we cannot know how
many keys a user has generated. However, we argue that this can in fact be very
close to reality, where a well-known issuer, after properly identifying a user,
attests the (possibly blinded) public key this user proves control of. Indeed,
our model and syntax support exactly this approach, by allowing users to
leverage previously obtained credentials in order to request new ones.
A consequence of this is that, if ``one user'' generates (e.g.) two keys, and
then uses each of these keys to request multiple credentials, then from the
point of view of our modelling, we see this \emph{cryptographically} as two
different users -- and, anyway, that same ``user'' cannot combine credentials
bound to different keys.

\paragraph{Users and issuers.} %
Finally, a relevant aspect of our approach is that users and issuers are
essentially the same thing: just an entity with a key pair. The difference is
that, when users wish to become issuers, they have to advertise their public
keys, along with their conditions for granting credentials. For simplicity, we
just assume that they somehow ``publish their public keys''. In practice, this
may be done in several ways, depending on the situation: self-signing, relying
on external PKIs, bulletin boards, etc.
%
This approach has actually been used before to model delegatable anonymous
credentials \cite{bcc+09}, and it turns out to be also very useful for our
approach to build ring signatures from \UAS.

@@

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all other functions.
\item[$\KeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, a user runs
  \KeyGen to generate its user key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given \parm, and the
  function \finsp, an opener runs \OKeyGen to generate its opening key pair.
  The function \finsp defines the type of utility that will be extractable from
  signatures.
\item[$\ISet(\upk,\usk,\fissue) \rightarrow \ipk$.] Given a user key
  pair, and an issuance function \fissue for checking that credential requestors
  meet some conditions to be issued a credential, an existing user runs \ISet to
  extend the user public key, enabling this user to issue credentials meeting
  \fissue.
%\item[$\UKeyGen(\parm) \rightarrow (\upk,\usk)$.] Given \parm, returns a user's
%  key pair.
\item[$\langle
  \Obtain(\usk,\cidu,\ipk,\sCred,\attrs),
  \Issue(\isk,\cidi,\sipk,\attrs))  
  \rangle \rightarrow \langle \Cred/\bot,R/\bot
  \rangle$.] %
  This interactive protocol lets a user with key \usk receive a credential
  $\Cred=(\cid,\attrs,\cred,\ipk)$
  from an issuer in the system. $\cid=(\cidi,\cidu)$ is a unique identifier for
  the credential, where issuer and user randomly pick \cidi and \cidu,
  respectively (to ease notation, whenever we write just \cid, we mean $(\cidi,
  \cidu)$). \ipk is the issuer's public key and \cred is the actual credential,
  on attribute set \attrs. The user may leverage a set of previously obtained
  credentials $\sCred=\lbrace (\cid_i=(\cidi_i,\cidu_i),\cattrs_i,\cred_i,
  \ipk_i)\rbrace_{i\in[n]}$, from which we may omit the $\ipk_i$s for
  readability. The user outputs the produced credential \Cred, while the issuer
  outputs $R \gets (\yissue,\utrans)$, for some value $\yissue$ output by
  the \fissue function defined by the issuer, and $\utrans$ being the transcript
  of the communication.
\item[$\Sign(\usk,\opk,\sCred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \sCred, a message \msg and evaluation function \feval, returns
  signature \sig, and a value \yeval. We use use \Sig to denote the
  tuple $(\sig,\yeval)$.
\item[$\Verify(\opk,\sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials by issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$, and a proof of
  correct opening \iproof.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We introduce three functions in our syntax and model. Through them,
it is possible to modulate the behaviour of the resulting instantiation, by
controling the conditions upon which a new credential can be issued, the
information revealed at signing time, or after signing. In all cases, it is
the user who computes them, and has to prove correctness of such computation.
We give concrete examples in \secref{sec:relationships}.

\begin{description}
\item[$\fissue: (\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)\rbrace_{i \in [n]})
  \rightarrow \yissue$.] Chosen
  by each issuer within a family of functions \famfissue, the issuance function
  defines the customized conditions required by the issuer to grant a credential
  with identifier $\cid = (\cidi,\cidu)$, over attributes \attrs, when requested
  by a user with public key \upk,
  leveraging a set of $n$ previously obtained credentials with identifiers and
  attributes given by $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$ (where
  $n$ may be $0$ if no previously obtained credential is used). \fissue returns
  a value $\yissue \in \rngfissue \cup \lbrace 0 \rbrace$, where we adopt the
  convention that $\yissue = 0$ means that the issuance request is denied; and
  $\yissue \neq 0$ means that the request is approved. \fissue functions must be
  \UAS-acceptable, as defined in \defref{def:uas-acc-func}.
\item[$\feval: (\upk,\lbrace(\cid_i,\cattrs_i)\rbrace_{i \in [n]},\msg)
  \rightarrow (\yeval^0,\yeval^1)$.] Signing evaluation functions, from a
  family of functions \famfeval, can be set on a per-signature basis. They
  receive the user public key \upk, a set of credentials with identifiers
  and attributes $\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]}$
  (where $n \ge 1$), and the message to be signed \msg. \feval outputs two
  values, $\yeval^0$ and $\yeval^1$. Both must belong in a well defined set
  \rngfeval. For readability, we write $\Yeval = (\yeval^0,\yeval^1)$.
\item[$\finsp: (\Yeval,\upk,\lbrace (\cid_i,\cattrs_i) \rbrace_{i \in [n]},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value (derived from the user's secret key,
  credentials' identifiers and attributes used for signing, and signed message)
  should be extractable by an opener. Its behaviour can be modulated by \Yeval,
  and it outputs a value \yinsp, which must belong in a well defined set
  \rngfinsp.
\end{description}

@@

\begin{figure}[ht!]
  \centering  
  \scalebox{0.9}{
    \procedure{$\Exp^{\UAS-acc-b}_\adv(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\upk,\usk) \gets \KeyGen(\parm) \\
      (\st,\attrs, \lbrace (\cidi,\cidu,\cattrs_i) \rbrace_{i\in[n]})
      \gets \adv(\upk) \\
      \pcif b=0:
      \yissue^* \gets \fissue(\upk,\cid,\attrs,\lbrace (\cid_i,\cattrs_i)
      \rbrace_{i\in[n]}) \\
      \pcelse: \yissue^* \getr \rngfissue \setminus \lbrace 0 \rbrace \\
      b^* \gets \adv(\st,\yissue^*) \\
      \pcreturn b^*
    }
  }
  \label{fig:uas-acceptable}
  \caption{Formal definition of \UAS-acceptable \fissue functions.}
\end{figure}

@@

\paragraph{Global Variables.} %
Users are referred to with user identifiers, \uid; for credentials, we use \cid;
and for openers, \oid. Although issuers are ``extended'' users, and thus can be
identified by their \uid, we also sometimes use \iid to refer to a user acting
as issuer, especially, for operations involving both a user and an issuer (this
also applies for key pairs).
%
For notational convenience, we often use these identifiers instead of the
corresponding user/issuer/opener keys.
%
All tables/sets are initialized as empty tables/sets. We use the following sets
and tables in our definitions:

@@

\begin{description}
% \item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
%   the associated issuance function.
\item[\HUGEN.] Adds a new honest user to the game, generating its keypair.
\item[\CUGEN.] Adds a new corrupt user to the game, setting its \upk to the
  value given by the adversary.  
\item[\OGEN.] Adds a new opener to the game, generating its key pair and
  setting its evaluation and inspection functions.
% \item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
%   key to the adversary.
\item[\ISET.] ``Upgrades'' a user to become an issuer, specifying its
  \fissue function.
\item[\UCORR.] Corrupts an existing (and honest) user, giving its secret
  key to the adversary. If the user was also an issuer, it becomes a corrupt
  issuer too.
\item[\OCORR.] Corrupts an existing (and honest) opener, by giving its secret
  key to the adversary.
% \item[\HUGEN.] Adds a new honest user to the game, by honestly generating
%   the user's key pair.
% \item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
%   user already exists and is honest, corrupts it, leaking its key and
%   credentials.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer, by
  letting it interact with honest users who want to receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures using credentials from honest
  users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\OBTCHALb.] Upon receiving a target credential identifier, two challenge
  users and credential sets, an honest issuer identifier, and a set of
  attributes, issues a credential for the challenge user and credential set
  defined by the bit $b$. 
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$.
\end{description}

@@

        \procedure{$\OBTCHALb(\cidu,\cuid_{0,1},\iid,\attrs,\cscid_{0,1}=$\\
          \hspace*{5.25em}$\lbrace (\ccid_{0,i},\ccid_{1,i}) \rbrace_{i\in[n]})$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[(\cdot,\cidu)] \neq \bot \lor
          \CCRED[(\cdot,\cidu)] \neq \bot: \pcreturn \bot \\
          \pcif \exists i\in[n]~\suchthat~
          \PUBIK[\cscid_{0,i}] \neq \PUBIK[\cscid_{1,i}]: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED: \\
          \pcind \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif 0(\fissue(\PUBUK[\cuid_0],(\cdot,\cidu),\attrs,\lbrace (\ccid_{0,i},\ATTR[\ccid_{0,i}])\rbrace_{i\in[n]})) \neq \\
          \pcind 0(\fissue(\PUBUK[\cuid_1],(\cdot,\cidu),\attrs,\lbrace (\ccid_{1,i},\ATTR[\ccid_{1,i}])\rbrace_{i\in[n]})):
          \pcreturn \bot \\
          \langle \Cred, \cdot \rangle \gets
          \langle \Obtain(\PRVUK[\cuid_b],\cidu,\PUBIK[\iid],\cscid_b,\attrs),
          \adv \rangle \\
          \CCRED[(\cdot,\cidu)] \gets (\cuid_b,\cred,\iid,\attrs,\cscid_b,\siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \centering
  \scalebox{0.9}{
    \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\uid,\oid,\scid,\msg,\feval)
      \gets \adv^{\HUGEN,\OGEN,\ISET,\OBTISS,\RREG}(\parm) \\
      \pcif \feval \notin \famfeval: \pcreturn 0 \\
      \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
      (\Sig = (\sig,\yeval)) \gets \Sign(\PRVUK[\uid],\PUBOK[\oid],\scid,\msg,
      \feval) \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
      \pcfor \cid \in \scid \pcdo: \\
      \pcind \textrm{Parse}~\CRED[\cid]~\textrm{as}~
      (\cdot,\cdot,\cdot,\attrs,n,\lbrace(\cid_i,\cdot)\rbrace_{i\in[n]})) \\
%      \pcind \textrm{Let}~\scid^{\cid}~\textrm{be the {\cid}s used to obtain}
%      ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,
%      \fissue^{\cid}),\cdot)\\
      \pcind \textrm{Parse}~\trans[\cid]~\textrm{as}~(\yissue,\utrans);
      \PUBIK[\cid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
      \pcind \pcif \fissue(\PUBUK[\uid],\cid,\attrs,
      (\lbrace(\cid_i,\ATTR[\cid_i])\rbrace_{i\in[n]})) \neq \yissue:
      \pcreturn 1 \\
      (\yeval^0,\yeval^1) \gets \feval(\PUBUK[\uid],(\scid,\ATTR[\scid]),\msg) \\
      \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0~\lor \\
      \pcind \yinsp \neq \finsp^\oid((\yeval,\yeval^1),
      \PUBUK[\uid],(\scid,\ATTR[\scid]),\msg)): \\
      \pcind \pcreturn 1 \\
      \pcreturn 0
    }
  }
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

The issuance anonymity game captures that, during credential issuance
interactions, the adversary gains no information about the
user(s) behind them. For this, we allow the adversary to control targetted
issuers and openers (although it may also add honest ones), and add honest and
corrupt users. The adversary can also obtain credentials, produce signatures,
and open them. We need to make some limitations to prevent trivial wins: first,
when querying the oracle for obtaining a challenge credential out of two
possible user-credential set pairs, the issuance protocol must either succeed or
fail for both; also, the adversary cannot mix challenge and non-challenge
credentials in the same call to the \SIGN oracle -- but can otherwise open
any signature. With these restrictions, if the adversary cannot distinguish
arbitrary runs with all oracles when he gets challenge credentials
$\cred_b$, from runs with credentials $\cred_{1-b}$, then the issuance protocol
is privacy-preserving.

@@

In this section, we give a generic construction of an \UAS scheme, based on
generic building blocks. We use three different NP relations:
\RelIss, \RelSig, and \RelIns, described next
and specified in CS notation \cite{cs97} in \figref{fig:nizkrels}.
